---
title: "Active Market Monitor"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: lumen
    orientation: rows
    css: style.css
---

<style>

.navbar-brand {
  display: grid;
  margin: auto;
  padding: 5px;
}

.navbar-author {
  margin-left: 0px;
}
</style>

```{r setup, include=FALSE}

#-----------------------------------------------------------------------
## FILE        : UI.R - USER INTERFACE             DATE : 19/08/2020
##
## CREATED BY  : Joshua Allen
##
## DESCRIPTION : Market monitor for US, CAD, EUR, YEN, AUS portfolios, including: 
##               yield and asset swap curves, carry/roll profiles of 
##               and more details view of the investment opportunity set 
##
## INPUTS      : start_date, end_date, REPO rates, MATURITY buckets 

# set config  -------------------------------------------------------

# source environment files
source("\\\\istdba/BuildArchive/ShinyApps/EnvironmentScript/EnvironmentScript_Latest/LOCAL/Artifactory/environment.R")

#set base directories
database_filename <- file.path("N:/Offdata/RM/_Data/ListManagement/list_membership.db")

# boe checkpoint
checkpoint_date <- "2022-01-01"
message(paste0("checkpoint_date: ", checkpoint_date))
boeCheckpoint(checkpoint_date, scanForPackages = FALSE)

# load packages -----------------------------------------------------

library(data.table)
library(DT)
library(lubridate)
library(tidyverse)
library(readr)
library(RSQLite)
library(jrvFinance)
library(sparkline)
library(formattable)
library(Rblpapi)
library(httr)
library(zoo)
library(flexdashboard)
library(ggplot2)
library(janitor)
library(plotly)
library(magrittr)
library(timeDate)

options(digits = 2)
options(DT.fillContainer = T)
options(scipen = 999)

# Load a library so that boeCheckpoint won't complain about it being missing
FIRVr_str <- "library(FIRVr, lib.loc = 'N:/Offdata/RM/_R code repository/RMPackages/_R4.0')"
eval(parse(text=FIRVr_str))


# souce functions ---------------------------------------------------------

source(file.path("../functions/functions.R"))
source(file.path("../config/config.R"))

# set paramters -------------------------------------------------------

# 1. set start/end dates in the format YYYY-MM-DD
start_date =  Sys.Date() - 1.5*360 # start date - default today - 270 days, need this for vol adjusted C+R (times series calc with 2m look back period)
end_date = Sys.Date() # end date - default today
DATE_START <- as.Date(start_date, "%d-%m-%Y")
DATE_END <-  as.Date(end_date, "%d-%m-%Y")

#2. set MATURITY buckets
Buckets = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 15, 20, 25, 30, 40)

# choose benchmark securities for each ortfolio, for carry/roll calculations
BENCHMARK_SECURITY_CAD = "CAN"
BENCHMARK_SECURITY_USD = "T"
BENCHMARK_SECURITY_EUR = "DE"
BENCHMARK_SECURITY_AUD = "ACGB"
BENCHMARK_SECURITY_JPY = "JGB"

# read in config file with defined lists 

config <- readr::read_csv(file = "../data/bond_lists.csv", show_col_types = FALSE)
provie_tickers <- config$PROVIES[!is.na(config$PROVIES)]  
aussie_tickers <- config$AUSSIE_STATES[!is.na(config$AUSSIE_STATES)] 
govie_tickers <- config$GOVIE_TICKERS[!is.na(config$GOVIE_TICKERS)]  
currencies <- config$CURRENCIES[!is.na(config$CURRENCIES)]  
bond_lists <- config$BOND_LISTS[!is.na(config$BOND_LISTS)]  

# source modules for report ----------------------------------------------
source("../modules/GET_DATA.R")
source("../modules/CARRY_ROLL.R")

```

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover(); 
});
</script>

Canada Curves {data-icon="fa-copyright"}
=====================================  

Row {data-height=500}
-------------------------------------

### Canada Curves

```{r CAD_CURVES, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "CAD", grouping = "TICKER")

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YLD_YTM_MID",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Canada Asset Swap Curves (CDOR)

```{r CAD_ASSET_SWAP, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "CAD", grouping = "TICKER")

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "ASSET_SWAP_SPD_MID",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Canada Spread to Government Curves

```{r CAD_GOV_SPREAD, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "CAD", grouping = "TICKER")


plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_ISPREAD_TO_GOVT",
  fill = "TICKER",
  polynomial_order = 3
)


```

Row {data-height=500}
-------------------------------------

### Canada Z-Spread ASW (CDOR)

```{r CAD_Z_SPREAD, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "CAD", grouping = "TICKER")

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_ISPREAD_TO_GOVT",
  fill = "TICKER",
  polynomial_order = 3
)

```

Canada C/R {data-icon="ion-android-refresh"}
=====================================  

Row {data-height= 750}
-------------------------------------

### Carry & Roll

```{r CAD_CarryRollPlot, out.width= "95%", out.height= "95%"}

p <-
  ScatterChart(cad_carry_roll,
               fill = "TICKER",
               xlab = "MATURITY",
               ylab = "CARRY_ROLL_12M") +
  ggplot2::geom_smooth(
    ggplot2::aes(
      x = MATURITY,
      y = CARRY_ROLL_12M,
      group = TICKER,
      colour = TICKER
    ),
    size = 0.2,
    method = "lm",
    se = F,
    formula = y ~ poly(x, 2, raw = TRUE)
  ) + ggplot2::theme(legend.title = element_blank())

plotly::ggplotly(p) %>%
  plotly_layout()

```

### By Issuer

```{r CAD_CarryRollProvince, out.width= "95%", out.height= "95%"}

data <- cad_carry_roll %>% 
  dplyr::group_by(TICKER, BUCKET) %>%
  dplyr::summarise(CARRY_ROLL_12M = mean(CARRY_ROLL_12M, na.rm = TRUE)) %>%
  dplyr::ungroup()

p <-
  barChart(
    data,
    xlab = "BUCKET",
    ylab = "CARRY_ROLL_12M",
    fill = "TICKER",
    position = "dodge"
  ) +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

### Component Contribution

```{r CAD_CarryRollContribution, out.width= "95%", out.height= "95%"}

data <- cad_carry_roll %>%
  dplyr::select(TICKER,  BUCKET,ROLL_1Y, CARRY_1Y) %>%
  tidyr::gather(key = Component, value = Value, -TICKER, -BUCKET) %>% 
  dplyr::group_by(TICKER, BUCKET, Component) %>% 
  dplyr::summarise(Value = mean(Value, na.rm = TRUE)) %>% 
  dplyr::ungroup() 

p <-
  barChart(data,
           xlab = "BUCKET",
           ylab = "Value",
           fill = "Component") + 
  ggplot2::facet_wrap( ~ TICKER)  +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

Row {data-height= 550}
-------------------------------------

```{r CAD_CarryRoll, out.width= "100%", out.height= "100%"}

df <- cad_carry_roll %>%
  dplyr::select(
    TICKER,
    CRNCY,
    ID_BB_SEC_NUM_DES,
    ISSUE_DT,
    MATURITY_YEARS,
    DURATION,
    YLD_YTM_MID,
    ASSET_SWAP_SPD_MID,
    Done,
    CARRY12M,
    ROLL_12M,
    CARRY_ROLL_12M
  ) %>%
  dplyr::rename("SECURITY" = "ID_BB_SEC_NUM_DES") %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>%
  tidyr::drop_na(CARRY12M, ROLL_12M, CARRY_ROLL_12M)

ism <- df %>% lapply(class) %>% unlist == "numeric"

create_data_table(
  df,
  row_group_index = 0
) %>% formatRound(ism, digits = 2) %>% 
  formatStyle(ism, color = styleInterval(0, c("red", "black"))) %>%
  formatStyle('CARRY12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%#
  formatStyle('ROLL_12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%
  formatStyle("CARRY_ROLL_12M", color = styleInterval(0, c("red", "green"))) 

```



US Curves {data-icon="fa-copyright"}
=====================================  

Row {data-height=500}
-------------------------------------

### US Treasury Curve

```{r UST_CURVE, out.width= "95%", out.height= "95%", warning=F, echo=F}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "USD", grouping = "TICKER") %>% 
  dplyr::filter(TICKER %in% c("T", "B", "CMB"))

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YLD_YTM_MID",
  fill = "YRS_TO_MTY_ISSUE",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### US ASW Curve (SOFR)

```{r UST_ASW, out.width= "95%", out.height= "95%", warning=F, echo=F}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "USD", grouping = "TICKER") %>% 
  dplyr::filter(TICKER %in% c("T", "B", "CMB"))

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "ASSET_SWAP_SPD_MID",
  fill = "YRS_TO_MTY_ISSUE",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### US Z-Spread ASW (SOFR)

```{r USA_ZSPREAD, out.width= "95%", out.height= "95%", warning=F, echo=F}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "USD", grouping = "TICKER") %>% 
  dplyr::filter(TICKER %in% c("T", "B", "CMB"))

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_ZSPREAD",
  fill = "YRS_TO_MTY_ISSUE",
  polynomial_order = 3
)
```

Row {data-height=1200}
-------------------------------------

### US SSA Asset Swap Curves (SOFR)

```{r USA_ASW_CURVES, out.width= "95%", out.height= "95%", warning=F, echo=F}

data <-
  all_securities %>% 
  dplyr:: mutate(ASSET_SWAP_SPD_MID = ASSET_SWAP_SPD_MID/100) %>% 
  dplyr:: filter(CRNCY == "USD", 
                 YLD_YTM_MID > 0,
                 MATURITY < Sys.Date() + 12 * 365, 
                 !TICKER %in% c("T", "B", "CMB")) %>% 
  tidyr::drop_na(ASSET_SWAP_SPD_MID)

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "USD", grouping = "TICKER") %>% 
  dplyr::filter(TICKER %in% c("T", "B", "CMB"), 
                MATURITY < Sys.Date() + 12 * 365) %>% 
  dplyr::rename("UST" = "TICKER") 


p <-
  plot_yield_curve_facets(
    data = data,
    data_facet = plot_data,
    xlab = "MATURITY",
    ylab = "ASSET_SWAP_SPD_MID",
    fill = "TICKER",
    fill_facet = "UST"
  ) +
  ggplot2::labs(x = NULL) + 
  ggplot2::facet_wrap( ~ TICKER, scales = "free", ncol = 3)

plotly::ggplotly(p)

```

US C/R {data-icon="ion-android-refresh"}
=====================================  

Row {data-height= 750}
-------------------------------------

### Carry & Roll

```{r US_CarryRollPlot, out.width= "95%", out.height= "95%"}

p <-
  ScatterChart(usa_carry_roll,
               fill = "TICKER",
               xlab = "MATURITY",
               ylab = "CARRY_ROLL_12M") +
  ggplot2::geom_smooth(
    ggplot2::aes(
      x = MATURITY,
      y = CARRY_ROLL_12M,
      group = TICKER,
      colour = TICKER
    ),
    size = 0.2,
    method = "lm",
    se = F,
    formula = y ~ poly(x, 2, raw = TRUE)
  ) + ggplot2::theme(legend.title = element_blank())

plotly::ggplotly(p) %>%
  plotly_layout()

```

### By Issuer

```{r US_CarryRollBar, out.width= "95%", out.height= "95%"}

data <- usa_carry_roll %>% 
  dplyr::group_by(TICKER, BUCKET) %>%
  dplyr::summarise(CARRY_ROLL_12M = mean(CARRY_ROLL_12M, na.rm = TRUE)) %>%
  dplyr::ungroup()

p <-
  barChart(
    data,
    xlab = "BUCKET",
    ylab = "CARRY_ROLL_12M",
    fill = "TICKER",
    position = "dodge"
  ) +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

### Component Contribution

```{r US_CarryRollContribution, out.width= "95%", out.height= "95%"}

data <- usa_carry_roll %>%
  dplyr::select(TICKER,  BUCKET,ROLL_1Y, CARRY_1Y) %>%
  tidyr::gather(key = Component, value = Value, -TICKER, -BUCKET) %>% 
  dplyr::group_by(TICKER, BUCKET, Component) %>% 
  dplyr::summarise(Value = mean(Value, na.rm = TRUE)) %>% 
  dplyr::ungroup() 

p <-
  barChart(data,
           xlab = "BUCKET",
           ylab = "Value",
           fill = "Component") + 
  ggplot2::facet_wrap( ~ TICKER)  +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

Row {data-height= 550}
-------------------------------------

```{r US_CarryRoll, out.width= "95%", out.height= "95%"}

df <- usa_carry_roll %>% 
  dplyr::select(
    TICKER,
    CRNCY,
    ID_BB_SEC_NUM_DES,
    ISSUE_DT,
    MATURITY_YEARS,
    DURATION,
    YLD_YTM_MID,
    ASSET_SWAP_SPD_MID,
    Done,
    CARRY12M,
    ROLL_12M,
    CARRY_ROLL_12M
  ) %>%
  dplyr::rename("SECURITY" = "ID_BB_SEC_NUM_DES") %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>%
  tidyr::drop_na(CARRY12M, ROLL_12M, CARRY_ROLL_12M)

ism <- df %>% lapply(class) %>% unlist == "numeric"

create_data_table(
  df,
  row_group_index = 0
) %>% formatRound(ism, digits = 2) %>% 
  formatStyle(ism, color = styleInterval(0, c("red", "black"))) %>%
  formatStyle('CARRY12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%#
  formatStyle('ROLL_12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%
  formatStyle("CARRY_ROLL_12M", color = styleInterval(0, c("red", "green"))) 

```


Euro Curves {data-icon="fa-copyright"}
=====================================  

Row {data-height=500}
-------------------------------------

### Euro Govie Curves

```{r EUR_CURVES, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "EUR", grouping = "TICKER") %>% 
  dplyr::filter(!TICKER %in% provie_tickers)

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YLD_YTM_MID",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Euro Asset Swap Curves (ESTR)

```{r EURO_ASSET_SWAP, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "EUR", grouping = "TICKER") %>% 
  dplyr::filter(!TICKER %in% provie_tickers)

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_O_SPREAD",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Euro Spread to Government Curves

```{r EUR_GOV_SPREAD, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "EUR", grouping = "TICKER") %>% 
  dplyr::filter(!TICKER %in% provie_tickers)

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_ISPREAD_TO_GOVT",
  fill = "TICKER",
  polynomial_order = 3
)


```

Row {data-height=500}
-------------------------------------

### Euro Z-Spread ASW (EURIBOR)

```{r EURO_ASW_ZSPREAD, out.width= "95%", out.height= "95%"}

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "EUR", grouping = "TICKER") %>% 
  dplyr::filter(!TICKER %in% provie_tickers)

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "ASSET_SWAP_SPD_MID",
  fill = "TICKER",
  polynomial_order = 3
)

```


Row {data-height=850}
-------------------------------------

### Euro SSA Asset Swap Curves (ESTR)

```{r EUR_SSA_CURVES, out.width= "95%", out.height= "95%", warning=F, echo=F}

data <-
  all_securities %>% 
  dplyr:: mutate(ASSET_SWAP_SPD_MID = ASSET_SWAP_SPD_MID/100) %>% 
  dplyr:: filter(CRNCY == "EUR", 
                 YLD_YTM_MID > 0,
                 MATURITY < Sys.Date() + 12 * 365, 
                 !TICKER %in% c(govie_tickers), 
                 !grepl(pattern = "TB", x = TICKER, ignore.case = T)) %>% 
  tidyr::drop_na(ASSET_SWAP_SPD_MID)

plot_data <- get_govie_data(data = government_bonds, CURRENCY = "EUR", grouping = "TICKER") %>% 
  dplyr::filter(TICKER %in% "DE",
                MATURITY < Sys.Date() + 12 * 365) %>% 
  dplyr::rename("DU" = "TICKER") 

p <-
  plot_yield_curve_facets(
    data = data,
    data_facet = plot_data,
    xlab = "MATURITY",
    ylab = "YAS_O_SPREAD",
    fill = "TICKER",
    fill_facet = "DU"
  ) +
  ggplot2::labs(x = NULL) + 
  ggplot2::facet_wrap( ~ TICKER, scales = "free", ncol = 3)

plotly::ggplotly(p)

```

Euro C/R {data-icon="ion-android-refresh"}
=====================================  

Row {data-height= 750}
-------------------------------------

### Carry & Roll

```{r Eur_CarryRollPlot, out.width= "95%", out.height= "95%"}

p <-
  ScatterChart(eur_carry_roll,
               fill = "TICKER",
               xlab = "MATURITY",
               ylab = "CARRY_ROLL_12M") +
  ggplot2::geom_smooth(
    ggplot2::aes(
      x = MATURITY,
      y = CARRY_ROLL_12M,
      group = TICKER,
      colour = TICKER
    ),
    size = 0.2,
    method = "lm",
    se = F,
    formula = y ~ poly(x, 2, raw = TRUE)
  ) + ggplot2::theme(legend.title = element_blank())

plotly::ggplotly(p) %>%
  plotly_layout()

```

### By Issuer

```{r EUR_CarryRollBar, out.width= "95%", out.height= "95%"}

data <- eur_carry_roll %>% 
  dplyr::group_by(TICKER, BUCKET) %>%
  dplyr::summarise(CARRY_ROLL_12M = mean(CARRY_ROLL_12M, na.rm = TRUE)) %>%
  dplyr::ungroup()

p <-
  barChart(
    data,
    xlab = "BUCKET",
    ylab = "CARRY_ROLL_12M",
    fill = "TICKER",
    position = "dodge"
  ) +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

### Component Contribution

```{r EUR_CarryRollContribution, out.width= "95%", out.height= "95%"}

data <- eur_carry_roll %>%
  dplyr::select(TICKER,  BUCKET,ROLL_1Y, CARRY_1Y) %>%
  tidyr::gather(key = Component, value = Value, -TICKER, -BUCKET) %>% 
  dplyr::group_by(TICKER, BUCKET, Component) %>% 
  dplyr::summarise(Value = mean(Value, na.rm = TRUE)) %>% 
  dplyr::ungroup() 

p <-
  barChart(data,
           xlab = "BUCKET",
           ylab = "Value",
           fill = "Component") + 
  ggplot2::facet_wrap( ~ TICKER)  +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

Row {data-height= 550}
-------------------------------------

```{r EUR_CarryRoll, out.width= "95%", out.height= "95%"}

df <- eur_carry_roll %>%
    dplyr::select(
    TICKER,
    CRNCY,
    ID_BB_SEC_NUM_DES,
    ISSUE_DT,
    MATURITY_YEARS,
    DURATION,
    YLD_YTM_MID,
    ASSET_SWAP_SPD_MID,
    Done,
    CARRY12M,
    ROLL_12M,
    CARRY_ROLL_12M
  ) %>%
  dplyr::rename("SECURITY" = "ID_BB_SEC_NUM_DES") %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>%
  tidyr::drop_na(CARRY12M, ROLL_12M, CARRY_ROLL_12M)

ism <- df %>% lapply(class) %>% unlist == "numeric"

create_data_table(
  df,
  row_group_index = 0
) %>% formatRound(ism, digits = 2) %>% 
  formatStyle(ism, color = styleInterval(0, c("red", "black"))) %>%
  formatStyle('CARRY12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%#
  formatStyle('ROLL_12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%
  formatStyle("CARRY_ROLL_12M", color = styleInterval(0, c("red", "green"))) 

```

Aussie Curves {data-icon="fa-copyright"}
=====================================  

Row {data-height=500}
-------------------------------------

### Aussie Govie Curves

```{r AUS_CURVES, out.width= "95%", out.height= "95%"}

plot_data <-
  get_govie_data(
    data = all_securities %>% dplyr::filter(CRNCY %in% "AUD", TICKER %in% c(aussie_tickers, govie_tickers)),
    CURRENCY = "AUD",
    grouping = "TICKER"
  ) 

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YLD_YTM_MID",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Aussie Asset Swap Curves (BBSW3M)

```{r AUD_ASSET_SWAP, out.width= "95%", out.height= "95%"}

plot_data <-
  get_govie_data(
    data = all_securities %>% dplyr::filter(CRNCY %in% "AUD", TICKER %in% c(aussie_tickers, govie_tickers)),
    CURRENCY = "AUD",
    grouping = "TICKER"
  ) 

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "ASSET_SWAP_SPD_MID",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Aussie Z-Spread Asset Swap Curves (BBSW3M)

```{r AUD_ASSET_ZSPREAD, out.width= "95%", out.height= "95%"}

plot_data <-
  get_govie_data(
    data = all_securities %>% dplyr::filter(CRNCY %in% "AUD", TICKER %in% c(aussie_tickers, govie_tickers)),
    CURRENCY = "AUD",
    grouping = "TICKER"
  ) 

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_ZSPREAD",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Aussie Spread to Government Curves

```{r AUS_GOV_SPREAD, out.width= "95%", out.height= "95%"}

plot_data <-
  get_govie_data(
    data = all_securities %>% dplyr::filter(CRNCY %in% "AUD", TICKER %in% c(aussie_tickers, govie_tickers)),
    CURRENCY = "AUD",
    grouping = "TICKER"
  ) 

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_ISPREAD_TO_GOVT",
  fill = "TICKER",
  polynomial_order = 3
)


```


Row {data-height=600}
-------------------------------------

### Aussie SSA Asset Swap Curves (BBSW3M)

```{r AUD_SSA_CURVES, out.width= "95%", out.height= "95%", warning=F, echo=F}

data <-
  all_securities %>%
  dplyr::mutate(ASSET_SWAP_SPD_MID = ASSET_SWAP_SPD_MID / 100) %>%
  dplyr::filter(
    CRNCY == "AUD",
    !TICKER %in% c(aussie_tickers, provie_tickers, "ACGB"),
    MATURITY < Sys.Date() + 12 * 365,
    !grepl(pattern = "TB", x = TICKER,ignore.case = T
    )
  ) %>%
  tidyr::drop_na(ASSET_SWAP_SPD_MID)

plot_data <-
  get_govie_data(data = government_bonds,
                 CURRENCY = "AUD",
                 grouping = "TICKER") %>%
  dplyr::filter(TICKER %in% "ACGB",
                MATURITY < Sys.Date() + 12 * 365) %>%
  dplyr::rename("ACGB" = "TICKER") 

p <-
  plot_yield_curve_facets(
    data = data,
    data_facet = plot_data,
    xlab = "MATURITY",
    ylab = "ASSET_SWAP_SPD_MID",
    fill = "TICKER",
    fill_facet = "ACGB"
  ) +
  ggplot2::labs(x = NULL) + 
  ggplot2::facet_wrap( ~ TICKER, scales = "free", ncol = 3)

plotly::ggplotly(p)

```



Aussie C/R {data-icon="ion-android-refresh"}
=====================================  

Row {data-height= 750}
-------------------------------------

### Carry & Roll

```{r AUD_CarryRollPlot, out.width= "95%", out.height= "95%"}

p <-
  ScatterChart(aud_carry_roll,
               fill = "TICKER",
               xlab = "MATURITY",
               ylab = "CARRY_ROLL_12M") +
  ggplot2::geom_smooth(
    ggplot2::aes(
      x = MATURITY,
      y = CARRY_ROLL_12M,
      group = TICKER,
      colour = TICKER
    ),
    size = 0.2,
    method = "lm",
    se = F,
    formula = y ~ poly(x, 2, raw = TRUE)
  ) + ggplot2::theme(legend.title = element_blank())

plotly::ggplotly(p) %>%
  plotly_layout()

```

### By Issuer

```{r AUD_CarryRollProvince, out.width= "95%", out.height= "95%"}

data <- aud_carry_roll %>% 
  dplyr::group_by(TICKER, BUCKET) %>%
  dplyr::summarise(CARRY_ROLL_12M = mean(CARRY_ROLL_12M, na.rm = TRUE)) %>%
  dplyr::ungroup()

p <-
  barChart(
    data,
    xlab = "BUCKET",
    ylab = "CARRY_ROLL_12M",
    fill = "TICKER",
    position = "dodge"
  ) +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

### Component Contribution

```{r AUD_CarryRollContribution, out.width= "95%", out.height= "95%"}

data <- aud_carry_roll %>%
  dplyr::select(TICKER,  BUCKET,ROLL_1Y, CARRY_1Y) %>%
  tidyr::gather(key = Component, value = Value, -TICKER, -BUCKET) %>% 
  dplyr::group_by(TICKER, BUCKET, Component) %>% 
  dplyr::summarise(Value = mean(Value, na.rm = TRUE)) %>% 
  dplyr::ungroup() 

p <-
  barChart(data,
           xlab = "BUCKET",
           ylab = "Value",
           fill = "Component") + 
  ggplot2::facet_wrap( ~ TICKER)  +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

Row {data-height= 550}
-------------------------------------

```{r AUD_CarryRoll, out.width= "95%", out.height= "95%"}

df <- aud_carry_roll %>% 
    dplyr::select(
    TICKER,
    CRNCY,
    ID_BB_SEC_NUM_DES,
    ISSUE_DT,
    MATURITY_YEARS,
    DURATION,
    YLD_YTM_MID,
    ASSET_SWAP_SPD_MID,
    Done,
    CARRY12M,
    ROLL_12M,
    CARRY_ROLL_12M
  ) %>%
  dplyr::rename("SECURITY" = "ID_BB_SEC_NUM_DES") %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>%
  tidyr::drop_na(CARRY12M, ROLL_12M, CARRY_ROLL_12M)

ism <- df %>% lapply(class) %>% unlist == "numeric"

create_data_table(
  df,
  row_group_index = 0
) %>% formatRound(ism, digits = 2) %>% 
  formatStyle(ism, color = styleInterval(0, c("red", "black"))) %>%
  formatStyle('CARRY12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%#
  formatStyle('ROLL_12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%
  formatStyle("CARRY_ROLL_12M", color = styleInterval(0, c("red", "green"))) 

```



Japan Curves {data-icon="fa-copyright"}
=====================================  

Row {data-height=500}
-------------------------------------

### Japan Govie Curves

```{r JPY_CURVES, out.width= "95%", out.height= "95%"}

plot_data <-
  get_govie_data(
    data = government_bonds,
    CURRENCY = "JPY",
    grouping = "TICKER"
  ) 

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_BOND_YLD",
  fill = "TICKER",
  polynomial_order = 3
)

```

Row {data-height=500}
-------------------------------------

### Japan Asset Swap Curves (TONAR)

```{r JPY_ASSET_SWAP, out.width= "95%", out.height= "95%"}

plot_data <-
  get_govie_data(
    data = government_bonds,
    CURRENCY = "JPY",
    grouping = "TICKER"
  ) 

plot_yield_curve(
  data = plot_data,
  xlab = "MATURITY",
  ylab = "YAS_ASW_SPREAD",
  fill = "TICKER",
  polynomial_order = 3
)

```

Japan C/R {data-icon="ion-android-refresh"}
=====================================  

Row {data-height= 750}
-------------------------------------

### Carry & Roll

```{r JPY_CarryRollPlot, out.width= "95%", out.height= "95%"}

p <-
  ScatterChart(jpy_carry_roll,
               fill = "TICKER",
               xlab = "MATURITY",
               ylab = "CARRY_ROLL_12M") +
  ggplot2::geom_smooth(
    ggplot2::aes(
      x = MATURITY,
      y = CARRY_ROLL_12M,
      group = TICKER,
      colour = TICKER
    ),
    size = 0.2,
    method = "lm",
    se = F,
    formula = y ~ poly(x, 2, raw = TRUE)
  ) + ggplot2::theme(legend.title = element_blank())

plotly::ggplotly(p) %>%
  plotly_layout()

```

### By Issuer

```{r JPY_CarryRollIssuer, out.width= "95%", out.height= "95%"}

data <- jpy_carry_roll %>% 
  dplyr::group_by(TICKER, BUCKET) %>%
  dplyr::summarise(CARRY_ROLL_12M = mean(CARRY_ROLL_12M, na.rm = TRUE)) %>%
  dplyr::ungroup()

p <-
  barChart(
    data,
    xlab = "BUCKET",
    ylab = "CARRY_ROLL_12M",
    fill = "TICKER",
    position = "dodge"
  ) +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

### Component Contribution

```{r JPY_CarryRollContribution, out.width= "95%", out.height= "95%"}

data <- jpy_carry_roll %>%
  dplyr::select(TICKER,  BUCKET,ROLL_12M, CARRY12M) %>%
  tidyr::gather(key = Component, value = Value, -TICKER, -BUCKET) %>% 
  dplyr::group_by(TICKER, BUCKET, Component) %>% 
  dplyr::summarise(Value = mean(Value, na.rm = TRUE)) %>% 
  dplyr::ungroup() 

p <-
  barChart(data,
           xlab = "BUCKET",
           ylab = "Value",
           fill = "Component") + 
  ggplot2::facet_wrap( ~ TICKER)  +
  ggplot2::scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  ggplot2:: theme(legend.title = element_blank())

plotly:: ggplotly(p) %>% 
  plotly_layout()

```

Row {data-height= 550}
-------------------------------------

```{r JPY_CarryRoll, out.width= "95%", out.height= "95%"}

df <- jpy_carry_roll %>% 
    dplyr::select(
    TICKER,
    CRNCY,
    ID_BB_SEC_NUM_DES,
    ISSUE_DT,
    MATURITY_YEARS,
    DURATION,
    YLD_YTM_MID,
    ASSET_SWAP_SPD_MID,
    Done,
    CARRY12M,
    ROLL_12M,
    CARRY_ROLL_12M
  ) %>%
  dplyr::rename("SECURITY" = "ID_BB_SEC_NUM_DES") %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>%
  tidyr::drop_na(CARRY12M, ROLL_12M, CARRY_ROLL_12M)

ism <- df %>% lapply(class) %>% unlist == "numeric"

create_data_table(
  df,
  row_group_index = 0
) %>% formatRound(ism, digits = 2) %>% 
  formatStyle(ism, color = styleInterval(0, c("red", "black"))) %>%
  formatStyle('CARRY12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%#
  formatStyle('ROLL_12M',
              backgroundColor = styleInterval(0, c('lightpink', 'lightgreen'))
  ) %>%
  formatStyle("CARRY_ROLL_12M", color = styleInterval(0, c("red", "green"))) 

```


